Verified Time Balancing of Security Protocols

### 2019-01-20 Src/talk.tex
Minor changes
minor changes

\begin{frame}[fragile]
  \frametitle{Formally Verifying a Time Balanced Security Protocol}
  \begin{itemize}
    \item Attackers can gain information from message timing.
    \item Can we model this invariant? Naively all operations 
          have the same running time.
    \item Can we ensure that assumptions on this model hold for the
            implementation?
  \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{Quick Background 1 - Currying}
  All functions treated as taking a single argument. \\ \\
  $f : \mathbb{N} \rightarrow \mathbb{N} \rightarrow \mathbb{N}$ \\
  $f = + $ \\ \\
  Applying an argument to a multi argument function returns the 
    rest of the function! (Arrow associates to the right)\\ \\
  $f(2) : \mathbb{N} \rightarrow \mathbb{N}$ \\
  $f(2) = 2 + $ \\ \\
  Finally all arguments are applied. \\ \\
  $f(2, 3) : \mathbb{N}$ \\
  $f(2, 3) = 2 + 3 = 5 $
\end{frame}

>>>>

\begin{frame}[fragile]
  \frametitle{Formally Verifying a Time Balanced Security Protocol}
  \begin{itemize}
    \item Attackers can gain information from message timing.
    \item Can we model a time-invariant protocol?
    \item A naive approach considers all operations have the 
          same running time.
    \item Can we ensure that assumptions on this model hold for the
            implementation?
  \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{Quick Background 1 - Currying}
  All functions treated as taking a single argument. \\ \\
  $f : \mathbb{N} \rightarrow (\mathbb{N} \rightarrow \mathbb{N}$) 
    \\
  $f = + $ \\ \\
  Applying an argument to a multi argument function returns the 
    rest of the function! (Arrow associates to the right)\\ \\
  $f(2) : \mathbb{N} \rightarrow \mathbb{N}$ \\
  $f(2) = 2 + $ \\ \\
  Finally all arguments are applied. \\ \\
  $f(2, 3) : \mathbb{N}$ \\
  $f(2, 3) = 2 + 3 = 5 $
\end{frame}
